Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-01-26 cogsci2016/paper.tex
new results
significativity

		\begin{figure}[h]
			\centering
			\includegraphics[width=8cm]{./include/tools.png}
			\caption{Play Environment}
			\label{env}
		\end{figure}

		\begin{figure}[h]
			\centering
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-16.pdf}}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-32.pdf}}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-49.pdf}}\\
			\hspace{-0.4cm}
			\subfloat{\includegraphics[width=8.8cm]{./include/dmp.pdf}}
			\caption{Exemple of one mouvement. Top: position of the arm at time steps 17, 33 and 50 along the $50$ steps movement. Bottom: value of the four Dynamical Movement Primitives during the movement.}
			\label{mvt}
		\end{figure}

@@

	\paragraph{}
	We measure the exploration of the different sensory spaces in the $6$ conditions each $5000$ iterations along the $300000$ iterations (Fig. \ref{res_explo}).
	We provide statistical Mann-Whitney U test results of comparisons of the exploration at the end of the experiments in different pairs of conditions.
	We first show that the Motor Babbling condition (H0-MB) quickly explores $S_{Hand}$ but explores badly the other sensory spaces, compared to the other conditions (STATS).
	Then H0-GB and H0-Tr have similar exploration results (STATS maybe Tr better in Boxes).
	Then H1-GR shows lower exploration of $S_{Hand}$, $S_{Stick_1}$ and $S_{Stick_2}$ than H0-GB and H0-Tr but higher exploration of $S_{Object}$ and $S_{Boxes}$ (STATS).
	Also, H1-GR shows lower exploration of all spaces than H1 (STATS).
	H1 shows lower exploration of $S_{Hand}$ than H0-GB and H0-Tr (STATS), similar (STATS?) exploration of $S_{Stick_1}$ and $S_{Stick_2}$ but higher exploration of $S_{Object}$ and $S_{Boxes}$ (STATS).
	H1-CL vs H1 (STATS?).

	\begin{figure*}[ht]
		\centering
		\subfloat{\includegraphics[width=14cm]{./include/xp1-explo-legend.eps}}\\
		\vspace{-0.3cm}
		\subfloat[$Hand$]{\includegraphics[width=3.5cm]{./include/xp1-explo-hand.eps}}
		\subfloat[$Stick_1$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_1.eps}}
		\subfloat[$Stick_2$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_2.eps}}
		\subfloat[$Object$]{\includegraphics[width=3.5cm]{./include/xp1-explo-obj.eps}}
		\subfloat[$Boxes$]{\includegraphics[width=3.5cm]{./include/xp1-explo-box.eps}}
		\caption{Exploration of sensory spaces.}
		\label{res_explo}
	\end{figure*}

>>>>

		\begin{figure}[h]
			\centering
			\hspace{-0.73cm}
			\vspace{-0.71cm}
			\includegraphics[width=9.12cm]{./include/tools.pdf}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-16.pdf}}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-32.pdf}}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-49.pdf}}\\
			\hspace{-0.42cm}
			\subfloat{\includegraphics[width=8.8cm]{./include/dmp.pdf}}
			\caption{Top: a state of the environment. Middle: position of the arm at time steps 17, 33 and 50 along the $50$ steps movement. Bottom: value of the four DMPs during the movement.}
			\label{env}
		\end{figure}

@@

	\paragraph{}
	We measure the exploration of the different sensory spaces in the $6$ conditions each $5000$ iterations along the $300000$ iterations (Fig. \ref{res_explo}).
	We provide statistical Mann-Whitney U test results of comparisons of the exploration at the end of the experiments in different pairs of conditions.
	We first show that the Motor Babbling condition (F-RmB) quickly explores $S_{Hand}$ and explores badly $S_{Object}$ and $S_{Boxes}$, compared to the other conditions ($p<0.0001$).
	Then F-RGB and F-AGB don't have significantly different exploration results in any space ($p>0.05$), 
	and explore less $S_{Stick_1}$, $S_{Stick_2}$, $S_{Object}$ and $S_{Boxes}$ than H-RGB-P-AMB condition ($p<0.05$).
	Also, H-RGB-GR-AMB shows lower exploration of $S_{Hand}$, $S_{Stick_2}$ and $S_{Object}$ than H-RGB-P-AMB ($p<0.05$).
	Condition H-RGB-P-AMB-PGITC explores more $S_{Hand}$ ($p<0.01$) and $S_{Stick_2}$ ($p<0.05$) than condition H-RGB-P-AMB.

	\begin{figure*}[ht]
		\centering
		\subfloat{\includegraphics[width=14cm]{./include/xp1-explo-legend.pdf}}\\
		\vspace{-0.3cm}
		\subfloat[$Hand$]{\includegraphics[width=3.5cm]{./include/xp1-explo-hand.pdf}}
		\subfloat[$Stick_1$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_1.pdf}}
		\subfloat[$Stick_2$]{\includegraphics[width=3.5cm]{./include/xp1-explo-stick_2.pdf}}
		\subfloat[$Object$]{\includegraphics[width=3.5cm]{./include/xp1-explo-obj.pdf}}
		\subfloat[$Boxes$]{\includegraphics[width=3.5cm]{./include/xp1-explo-box.pdf}}
		\caption{Exploration of sensory spaces.}
		\label{res_explo}
	\end{figure*}
